\chapter{Literature Review}
\label{LR}
In this chapter we will review the literature in two sections. The two sections, covering idiosyncratic volatility and financial forecasting models, can be perceived rather independent. In the next chapter, we will connect the two literature spaces in a dynamic ARMA-GARCH return forecasting model. 

\section{Idiosyncratic volatility}  
There exists various definitions of idiosyncratic volatility (IV). Malkiel and Xu \cite{malkielxu97} defined IV as the variance of stock return minus variance of the S\&P 500 index. Malkiel and Xu \cite{malkielxu04} and Bali and Cakici \cite{balicakici08} calculate the IV the standard deviation of the regression residual of both the CAPM and Fama-French three factor model \cite{famafrench}. The latter model was among others also adopted by Ang et al. \cite{angetal06} \cite{angetal09}  and Fu \cite{Fu}. Common for the various definitions are the description of IV as the fluctuations in the stock price caused by company-specific factors, with little or no correlation with market risk.

To further understand the theory behind and implications of IV, we will elaborate on literature exploring the pricing of risk factors and the empirical relationship between IV and stock returns.

\subsection{The pricing of risk factors}
The behaviour of stock returns, and the factors influencing them, have been extensively covered in literature. 

The Capital Asset Pricing Model (CAPM) presented by Sharpe \cite{sharpe} and Lintner \cite{litner}, is well-known for for its use to determine an asset's theoretical returns. The CAPM is a specific theory of the determinants of expected returns, and it says that all investors should hold the market portfolio to remove all idiosyncratic risk. However, according to Fu \cite{Fu}, some idiosyncratic risk is priced into their portfolios, since no investor holds perfectly diversified portfolios. Therefore, the analysis of idiosyncratic risk has become an important field of study.

Several studies have tried to extend the CAPM to price the idiosyncratic risk. Banz \cite{banz} introduced the size effect in stocks traded on the NYSE, which was the basis for the Fama and French \cite{famafrench}. They developed the Three-Factor Model, taking into account market, size and growth risks. Fama and French \cite{famafrench} conclude that their model explains returns better than the CAPM. However, Merton \cite{merton87} presented a theory that investors demand a higher expected return in compensation of higher idiosyncratic risk, as investors are not totally diversified. This layed the ground for the discovering the relationship between IV and returns.

\subsection{Relationship between idiosyncratic risk and returns}
The relationship between IV and future returns has been extensively studied. Literature shows that there is divided opinion of the existence of any relationship. Many studies indicate a positive relationship, while others find no, or even a negative one. We will now highlight results from both sides.

\subsubsection{Advocates of a positive relationship}
There exist several studies that conclude that idiosyncratic volatility is positively correlated with stocks' future returns. This conclusion comes from the idea of Merton \cite{merton87}, that non-diversified investors requires higher expected returns to justify increased risk. The foremost studies on this are Merton \cite{merton73} and Levy \cite{levy}.

Malkiel and Xu \cite{malkielxu02} indicate the positive relationship between IV and the cross-section of expected returns. They conclude that IV is more important than firm size in explaining the cross-section of returns. Malkiel and Xu \cite{malkielxu04} found a positive relationship using CAPM and the Fama- French three factor model \cite{famafrench}. The idiosyncratic volatility was not only positively related to the return but also a more powerful explanatory variable than the market return, size and value factors.
 
Additionally, Spiegel & Wang  \cite{spiegelwang} idiosyncratic volatility had a positive relationship with expected return, and a negative relationship with liquidity. In their sample the highest IV deciles had 1.33\% more average return than the lowest deciles. In addition, the highest deciles had the smallest size and the least liquidity in their result. Kotiaho \cite{kotiaho} carried out a similar study and found that especially small-cap stocks have a positive relationship between their IV and expected returns.

\subsubsection{Advocates of a negative relationship}
if IV is taken to represent firm-specific risk for an investor, it commands a premium, s IV proxying for something other than non-diversifiable risk

A positive relationship between risk and return is widely accepted in financial theory. Hence, if IV is interpreted as firm-specific risk for an investor, it commands a premium. However, in contrast to previous studies, in recent studies this interpretation has taken a new direction.

Ang et al. \cite{angetal09} presented some groundbreaking results. Using data from 23 countries (including Norway), they examined the cross-sectional relationship between IV and expected returns. They concluded that stocks with a higher IV earned lower expected returns, using the Fama-French three factor model \cite{famafrench}. In a previous article, Ang et al. \cite{angetal06} indicate a negative relationship between a stock's monthly returns and its 1-month lagged idiosyncratic risk. 

In our study we consider the relationship between a portfolio's daily IV and forecasting performance. Thus, Bali and Cakici \cite{balicakici06} study is interesting. They show that Ang et al. \cite{angetal09} results where not robust, with different estimation methods. They indicate no relation between value-weighted portfolio returns and the value-weighted average IV. However, Huang, Liu, Rhee, and Zhang \cite{huang} contest these and Ang et al. \cite{angetal09} results. Their analysis shows that there is a relation, and it can be explained by short-term mean-reversion.

Jiang et al. \cite{jiangetal} identifies some reasons for this unexpected reality, commonly defined as the idiosyncratic volatility anomaly. They argue that IV is a proxy of future earnings shocks and that the anomaly to a large extent is caused by corporate selective disclosure. 

In summary, there exists divided opinion on the relationship between idiosyncratic risk and stock returns. On the positive side, literature explains the positive relationship by the fact that investors cannot fully diversify their portfolio due to the information and transaction costs. Contrary, Ang et al. \cite{angetal06} among others, found a negative relationship between IV and expected return. Jiang et al. \cite{jiangetal} explains the anomaly by corporate selective disclosure.

\subsubsection{Studies on the relationship between idiosyncratic volatility and returns in the Norwegian stock market}

In the case of the Norwegian stock market, some studies have already analyzed the relationship between idiosyncratic risk and future returns. They focus to a large extent on the low idiosyncratic volatility anomaly introduced by Ang et al. \cite{angetal06}, which states that stocks with low IV tend to outperform stocks with high IV. 

Arnesen and Borge \cite{arnborge} examined the relation between idiosyncratic volatility and stock returns at the Oslo Stock Exchange. They find that stocks with low idiosyncratic volatility significantly outperform stocks with high idiosyncratic volatility in terms of Fama and French \cite{famafrench} alphas. They argue that firm size, skewness and illiquidity effects can explain the low returns of stocks with high idiosyncratic volatility.

Furthermore, Tjaum and Wiedswang \cite{thaumwiedswang} contribute with a measure of arbitrage activity for the idiosyncratic volatility strategy, which goes long stocks with low idiosyncratic- and short stocks with high idiosyncratic volatility. They conclude that the the low idiosyncratic volatility anomaly exist, but is decreasing with time and arbitrage activity. 

Contrary to the contributions above, Østnes and Hafskjær \cite{ostnes} document that the strong performance of low volatility stocks relative to high volatility stocks is not present in Norway. Their findings are robust for exposure to size, liquidity, momentum and book-to-market effects. They conclude that there is no low idiosyncratic volatility anomaly in Norway.


\section{Return forecasting models}

Financial time series prediction deals with the task of modelling the underlying data generation process using past observations to specify a model that extrapolates the time series into the future. Due to the intrinsic difficulty, widespread applications and potential economic gains of financial forecasting, much effort was devoted in the past few decades to the model specification. In the literature, there are some classical methods that have been developed in predicting financial time series. 

\subsection{Linear forecasting models}

In conventional econometric models, the variance of the disturbance is assumed to be constant. Among the linear time forecasting models is a powerful method, available in the literature for univariate time-series forecasting, known as Box and Jenkins ARMA approach on stationary time series \cite{B&J}. Despite its simplicity and versatility in modelling several types of linear relationship such as pure autoregressive (AR), pure moving average (MA) and autoregressive moving average (ARMA) series, such type of models was constrained by its linear scope. 

\subsection{Non-linear forecasting models}

Real-world systems are seldom linear. Many economic and financial time series such as exchange rates, stock market indices, market returns, inflation rate, etc. exhibit periods of unusual large volatility, followed by periods of relative tranquillity. Such circumstances suggest a form of heteroskedasticity in which the variance of the disturbance depends on the size of preceding disturbance and hence the conditional variance is non-constant over the sample period. 

\subsubsection{ARMA-GARCH}

Engle \cite{Engel} showed that it is possible to model the mean and the variance of a series simultaneously by a model named autoregressive conditional heteroskedastic (ARCH); whereas Box and Jenkins \cite{B&J} modelled only the conditional mean. Bollerslev \cite{Bollerslev} extended Engle’s \cite{Engel} original work by developing a technique that allows the conditional variance to be an ARMA process. The extended process is known as the GARCH process. Wong et al. \cite{Wetal} used the AR-GARCH in exchange rate prediction. Tang et al. \cite{Tetal} added the moving average part to the conditional mean equation and used the ARMA-GARCH model for stock price prediction. GARCH models is able to deal with common financial data time series characteristics such as thick tails, high peaks and volatility clustering, as pointed out by Mandelbrot \cite{Mandelbrot}. There are, however, some characteristics of financial time series that the GARCH model is not able to deal with. The main disadvantage of the GARCH model is that conditional variance depends on the squared value of the market shocks, which in turn means that the model is sensitive only to the absolute accuracy, precision of the variable but not to its sign leading to a presence of a leverage effect Black \cite{Black}, which represents a negative correlation between asset returns and volatility of returns. Evidence on the forecasting ability of the GARCH model is somewhat mixed. Anderson and Bollerslev \cite{A&B} showed that the GARCH model provides good volatility forecast. Conversely, some empirical studies, Brailsford and Faff \cite{f1}, Cumby et al. \cite{f2}, Figlewski \cite{f3},  Jorion \cite{f4}\cite{f5}, McMillan et al. \cite{f6}, have showed that the GARCH model tends to give poor forecasting performances. 

\subsubsection{Artificial Intelligence-based forecasting models}

To improve the forecasting ability over the ARMA-GARCH model, Artificial Intelligence-based techniques for forecasting financial time series has been advocated. Neural network is one such technique. The aforementioned forecasting models are based on some specific assumptions, such as linearity, or on error distributions, such as normality. When using neural networks to forecast financial time series, one do not need to make specific assumption. This, and the ability to approximate any nonlinear relationship with a reasonable degree of accuracy, has made the use of neural networks a popular forecasting algorithm. However, neural network suffers from a number of weaknesses including the need for a large number of controlling parameters, difficulty in obtaining a global solution and the danger of over-fitting.

Another Artificial Intelligence-based forecasting model based on support-vector machine, was developed by Vapnik \cite{Vapnik1}\cite{Vapnik2}. Since then it has been gaining popularity due to many attractive features. While the traditional neural network implements the empirical risk minimization principle, support-vector machine implements the structural risk minimization principle which seeks to minimize the upper bound of the population risk using the concept of the Vapnik–Chervonenkis dimension, as opposed to empirical risk minimization, that minimizes the error on the in-sample estimating data. Based on the structural risk minimization principle, support-vector machine achieves a balance between the training error and generalization error, leading to better forecasting performance than traditional neural network. Selecting the best model in support-vector machine is equivalent to solving a quadratic programming, which gives support-vector machine another merit of a unique global solution. 

In this paper we will use the ARMA-GARCH to forecast the one-day-ahead return. Review of artificial Intelligence based forecasting models are included in this chapter because the concept are further discussed in Chapter \label{FutureWork}.

In contrast to existing literature on IV and forecasting models, we will seek to contribute to existing literature by examining the relationship between the IV percentage and return forecasting performance. 
